Poster Data Analysis

### 2018-09-10 notebooks/poster_analysis.Rmd
added correlation plots for genes

>>>>

## Correlation plot for mutations in intrinsic genes
```{r}
corr_megares <- megares_results %>%
  select(-c(type, acrB)) %>%
  left_join(species_data, by = "id") %>%
  mutate(compl = complete.cases(.)) %>%
  filter(compl == TRUE) %>%
  split(., f = .$species) %>%
  lapply(., function(x) select(x, -c(species, id, compl)))

mut_corr_matrices <- lapply(corr_megares, function(x) create_corr_matrix(x)) %>%
  bind_rows(.id = "species")

ggplot(mut_corr_matrices, aes(var1, var2, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradientn(colors=cols,
                       na.value="grey95",
                       limits=c(-1, 1),
                       guide=guide_colourbar(ticks=T,nbin=10,
                                             barheight=.5,label=T, 
                                             barwidth=10))+
  labs(fill = NULL)+
  theme_classic()+
  theme(axis.text = element_text(size = 7),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4),
        axis.title = element_blank(),
        legend.position="bottom",
        legend.justification="center",
        legend.direction="horizontal")+
  coord_fixed()+
  facet_wrap(~species)
```

## Correlation plot for acquired genes
```{r message=FALSE, warning=FALSE}
corr_resfinder <- resfinder_results %>%
  select(-type) %>%
  left_join(species_data, by = "id") %>%
  split(., f = .$species) %>%
  lapply(., function(x) select(x, -c(species, id)))

acquired_corr_matrices <- lapply(corr_resfinder, function(x) create_corr_matrix(x)) %>%
  bind_rows(.id = "species")

ggplot(acquired_corr_matrices, aes(var1, var2, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradientn(colors=cols,
                       na.value="grey95",
                       limits=c(-1, 1),
                       guide=guide_colourbar(ticks=T,nbin=10,
                                             barheight=.5,label=T, 
                                             barwidth=10))+
  labs(fill = NULL)+
  theme_classic()+
  theme(axis.text = element_text(size = 6),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4),
        axis.title = element_blank(),
        legend.position="bottom",
        legend.justification="center",
        legend.direction="horizontal")+
  coord_fixed()+
  facet_wrap(~species)
```
